Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-08-31 WSSSPE3/report/JORS-reviews-responses.txt

Reviewer A:

Comments to the authors: 
	The paper summarizes the agenda, discussion, and outputs of the WSSSPE3.0
workshop on scientific software sustainability. The paper provides good
insight into the status of that discourse, very relevant to the JoRS venue.
Each section provides useful literature background and identifies people and
groups that readers can follow up with if they are interested in particular
topics. The inclusion of the longer appendices is very useful.  I have two
comments that would improve the article, neither of which I think are
crucial to publication but would be useful.

The paper lays out it's structure at the start, but each section could end
with additional signposts ("having done x, and before doing y, we will
review z"). I think those help the reader know where they are in a long
document.

RESPONSE: We’ve added some text at the start of Sections 4 and 5 to better
explain the workshop and report structure.

@@

Minor Comments:
1. I would avoid using the ableist term “bipolar” even if lifted
directly from the keynote;

RESPONSE: we've reworded this

2. I wonder if would be better to enhance the linking and referencing of
online materials in this document even beyond its already rich set of
footnoted links. For instance, all of the lightning talks refer to standing
proposals or active projects, but there are almost no reference URLs for
these projects or proposals;

RESPONSE: We have added a number of URLs (footnotes) and references to the
lightning talk paragraphs.

@@

3. There are many outlines in the appendices, and I’d like to note that
some outlines in the WSSSPE2 JORS article were negatively affected by poor
typesetting. You might want to make sure JORS gets them all right.

RESPONSE: The JORS typesetting process is a bit different than that of
traditional journals, but we will strive to pay attention to this and ensure
that it is correct.

### 2016-08-31 WSSSPE3/report/WSSSPE3_review.tex
adding Patra ref/cite

\item \textbf{Abani Patra, Hossein Aghakhani, Nikolay Simakov, Matthew Jones,
and Tevfik Kosar: \textit{Integrating New Functionality Using Smart Interfaces
to Improve Productivity of Legacy Tools}}. Abani Patra presented an example of
how the community using Titan2D, a geoflow simulation software, increased the
productivity of their tools by improving both code and data layout. The main
obstacles in this change were the non-existence of a common version control
system for the source code, coupled with multiple versions of the same code
base, the fixed format of input files, that many input values were set as
compilation flags, and that the internal data layout was not suitable for modern
technologies (e.g., vectorization, accelerators). The approaches of the Titan2D
developers included reinforcing the code structure using multiple layers of
Python and C++ interfaces, and a redesign of the data layout to be more suitable
for modern CPUs and accelerators.

>>>>

\item \textbf{Abani Patra, Hossein Aghakhani, Nikolay Simakov, Matthew Jones,
and Tevfik Kosar: \textit{Integrating New Functionality Using Smart Interfaces
to Improve Productivity of Legacy Tools}}. Abani Patra presented an example of
how the community using Titan2D, a geoflow simulation software, increased the
productivity of their tools by improving both code and data layout~\cite{Patra20051}. The main
obstacles in this change were the non-existence of a common version control
system for the source code, coupled with multiple versions of the same code
base, the fixed format of input files, that many input values were set as
compilation flags, and that the internal data layout was not suitable for modern
technologies (e.g., vectorization, accelerators). The approaches of the Titan2D
developers included reinforcing the code structure using multiple layers of
Python and C++ interfaces, and a redesign of the data layout to be more suitable
for modern CPUs and accelerators.
